% !TEX root = ../thesis.tex
%*******************************************************
% Acknowledgements
%*******************************************************
% \pdfbookmark[1]{Acknowledgements}{Acknowledgements}

% \bigskip

% \begingroup
% \let\clearpage\relax
% \let\cleardoublepage\relax
% \let\cleardoublepage\relax

\phantomsection
\manualmark
\markboth{\spacedlowsmallcaps{Acknowledgements}}{\spacedlowsmallcaps{Acknowledgements}}
\addcontentsline{toc}{chapter}{\tocEntry{Acknowledgements}}

\chapter*{Acknowledgements}

\begin{chapquote}{Marcel Proust, \textsc{Les plaisirs et les jours}}
Soyons reconnaissants aux personnes qui nous donnent du bonheur, elles sont les charmants jardiniers par qui nos âmes sont fleuries.
\end{chapquote}

I am immensely grateful to my two PhD supervisors, Lora Aroyo and Chris Welty, for your mentorship, guidance and patience. Thank you Lora for pushing me outside of my comfort zone and encouraging me to reach for the big, meaningful (also more challenging) research questions, and not settle for less. You supported me in my work since you supervised my Master's thesis, and I would not be here without you. Chris, thank you for all the opportunities you created for me, mentoring me through two internships that taught me research does not need to be confined in academia. Getting stuck in an experiment is the most difficult part of doing a PhD, but with your guidance I always managed to find a way forward.

I would like to thank my thesis committee: Michel Dumontier, Patricia Lago, Massimo Poesio, Elena Simperl and Piek Vossen, for the time and effort spent reading this thesis. I am honored for the opportunity to defend my thesis in front of you.

I would have never been able to realize this work without the help and support of Oana, Benjamin, and all the other members of the CrowdTruth team. So many of the ideas in this book came out of talking to you, during our work meetings, reading groups, even casual chit chat. Our work together will always be one of the high points in my professional career, and a very fond memory.

Thank you to Robert-Jan, Zoltán, Manfred, and all of the former and current members of IBM CAS. You not only financially supported my work through the IBM PhD Fellowship, you taught me the value of trying to bring research into the real world, and also the challenges that come with addressing problems outside of academia. I will always be grateful for the opportunity to have worked together with you at the Watson class - the most difficult and rewarding teaching project I was involved in.

To Astrid and Dena, thank you for your friendship and for being there through all the highs and lows. To Cristina, Victor, Tobias, Mojca, Ronald, Chris, Niels, Jacco, Archana, and all former and current colleagues in the User Centric Data Science group, thank you for being my community and for making me and my work feel like a part of something bigger. I am lucky to have had you as my academic family. To Filip, Julienka, Antske, Peter, Albert, Sara, and all the other members of the KRR group at the VU, as well as the broader Artificial Intelligence faculty - thank you for expanding my horizons into weird exciting new directions.

My two industry internships have been a formative experience of my PhD for which I am immensely grateful. Thank you to Anthony Levas and Ken Barker from IBM Watson, and Kishore Papineni from Google AI for welcoming me into your research groups. The experience of working with you has been invaluable.

Thank you to Roxana for the beautiful cover of this thesis, to David for the Dutch translation of the thesis summary, and to Dan for helping out with the Romanian version. Thank you to my parents for always pushing me become the best version of myself - vă mulțumesc! Thank you to my brother Dudu, for keeping me grounded and for always making me laugh. Thank you to my family, for always being there for me. To the 188F collective, past and present, thank you for supporting me in the tough moments, and not minding too much the complaining about academic matters. To Anastasia, thank you for the solidarity. And last but not least, thank you Rik for all your patience, your kindness and your kaasstengels.

\bigskip

\begin{flushright}
Amsterdam, July 2019
\end{flushright}

\vfill

% \endgroup
